---
output: 
  md_document:
    variant: gfm
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# bootstrapFP

[![CRAN\_Status\_Badge](https://www.r-pkg.org/badges/version/bootstrapFP)](https://cran.r-project.org/package=bootstrapFP)
[![](https://cranlogs.r-pkg.org/badges/grand-total/bootstrapFP)](https://cran.r-project.org/package=bootstrapFP)


## Description

This package provides bootstrap algorithms for Finite Population inference, for
estimating the variance of the Horvitz--Thompson estimator.


## Installation

To install the package from CRAN, run the following code in *R*:
``` r
install.packages("bootstrapFP")
```

Or, for the development version:
``` r
# if not present, install 'devtools' package
install.packages("devtools")
devtools::install_github("rhobis/bootstrapFP")
```

## Usage

```{r usage, eval=FALSE}
library(bootstrapFP) 

### Generate population data ---
N   <- 20; n <- 5
x   <- rgamma(N, scale=10, shape=5)
y   <- abs( 2*x + 3.7*sqrt(x) * rnorm(N) )
pik <- n * x/sum(x)

### Draw a dummy sample ---
s  <- sample(N, n)

### Estimate bootstrap variance ---
bootstrapFP(y = y[s], pik = n/N, B=100, method = "ppSitter")
bootstrapFP(y = y[s], pik = pik[s], B=10, method = "ppHolmberg", design = 'brewer')
bootstrapFP(y = y[s], pik = pik[s], B=10, D=10, method = "ppChauvet")
bootstrapFP(y = y[s], pik = n/N, B=10, method = "dRaoWu")
bootstrapFP(y = y[s], pik = n/N, B=10, method = "dSitter")
bootstrapFP(y = y[s], pik = pik[s], B=10, method = "dAntalTille_UPS", design='brewer')
bootstrapFP(y = y[s], pik = n/N, B=10, method = "wRaoWuYue") 
bootstrapFP(y = y[s], pik = n/N, B=10, method = "wChipperfieldPreston")
bootstrapFP(y = y[s], pik = pik[s], B=10, method = "wGeneralised", distribution = 'normal')
```


## More

- Please, report any bug or issue [here](https://github.com/rhobis/bootstrapFP/issues).
- For more information, please contact the maintainer at `roberto.sichera@unipa.it`. 
